Effect of resonant and random excitation on the LHC beam in the context of pulsed hollow electron lens operation.

### 2018-02-16 resex.tex
Revised section on fields in overlap region

For a perfectly annular and axially symmetric profile, the field in
the region of the proton beam core vanishes as can be seen from
Eq.~\ref{eq:field_2} and as illustrated in
Fig.~\ref{fig:hel_field}. Fields at the location of the proton beam
core thus only arise in case of profile imperfections of the electron
beam, in particular if the axial symmetry is broken. Recently, the
latest LHC hollow electron gun prototype was characterized at the
Fermilab electron lens test stand \cite{hel_test_stand_fnal}. A
typical measurement of the electron beam current density is shown in
Fig.~\ref{core:fig:0}.

As at the test stand the solenoidal fields required for the HL-LHC
electron lens can not be reached, an estimate of the electron beam
profile for HL-LHC can only be obtained through simulations. For this
purpose, the measured distribution is compressed to the inner electron
beam radius of 1.24~mm. Afterwards an input distribution with
$40\ 000$ particles is generated. As boundary condition, the LHC inner
beam pipe radius $b=30$~mm is used. The potential and fields can then
be calculated with the particle in cell simulation code
Warp~\cite{warp} yielding the relative electric field strengths shown
in Fig.~\ref{core:fig:1}. The electric field can in general be scaled
with the beam current and energy, but can not easily be scaled with
the inner and outer radius of the electron beam
distribution. Therefore it is essential to track a distribution with
the correct dimensions. Further details on the measurements and Warp
simulations can be found in~\cite{hel_res_field_stancari_2017}.

Using these measurements and calculations of the relative electric field strengths in the transverse plane (Fig.~\ref{core:fig:1}), we obtain an average field in the hole of
\begin{equation}
	E_{\mathrm{rel}}= 5\%
\end{equation}
For a maximum kick of $392$~nrad as derived in Eq.~\ref{eqn:helkick}, the estimated dipole kick amplitude at the proton beam core then is:
\begin{equation}\label{eqn:kick_central}
\Delta x'_{\rm{central \ region}}, \Delta y'_{\rm{central \ region}} = \SI{20}{nrad}
\end{equation}

>>>>

For a perfectly annular and axially symmetric profile, the field in
the region of the proton beam core vanishes. This is expressed by
Eq.~\ref{eq:field_2} and is illustrated in
Fig.~\ref{fig:hel_field}. Fields at the location of the proton beam
core can arise in case of profile imperfections of the electron
beam, in particular if the axial symmetry is broken.

Recently, a hollow electron gun prototype for the LHC (called CHG1b)
was characterized at the Fermilab electron lens test
stand~\cite{hel_test_stand_fnal}. An example of a measurement of the
electron beam current density is shown in Fig.~\ref{core:fig:0}.

In the test stand, only resistive solenoids are available. Through
simulations, one can estimate the fields generated by the compressed
electron beam profile needed for HL-LHC. The measured distribution is
compressed to the inner electron beam radius of 1.24~mm, corresponding
to $4\sigma_p$, as described in Table~\ref{tab:hllhc_param} and
Table~\ref{tab:hel_param}. A distribution with about $65\,000$
particles is generated according to the measured current-density
profile. As boundary condition, the LHC inner beam pipe radius
$b=30$~mm is used. The potential and fields are then calculated with
the particle-in-cell code Warp~\cite{warp}. The resulting relative
electric field strengths are shown in Fig.~\ref{core:fig:1}. The
electric field is obviously proportional to the charge density of
electrons. Its relative strength is rather insensitive to the hollow
beam radii, as long as these remain small compared to the beam pipe
radius. Further details on the measurements and Warp simulations can
be found in Ref.~\cite{hel_res_field_stancari_2017}.

Using these measurements and calculations of the relative electric
field strengths in the transverse plane (Fig.~\ref{core:fig:1}), we
obtain an average field in the hole of

\begin{equation}
  E_{\mathrm{rel}}= 5\%.
\end{equation}

For a maximum kick of 392~nrad, as derived in Eq.~\ref{eqn:helkick},
the estimated dipole kick amplitude at the proton beam core is then

\begin{equation}
  \label{eqn:kick_central}
  \Delta x'_{\rm{central \ region}}, \Delta y'_{\rm{central \ region}} = \SI{20}{nrad}.
\end{equation}

For the scope of this paper, only the approximate magnitude of the
residual dipole kick is considered. In general, the field map,
including its multipolar components, can be parameterized in a
symplectic form, as described for instance in
Ref.~\cite{hel_bends_stancari}, and used in tracking codes to estimate
the effects on the circulating beam.
